Re-finding to support a Deep Web Question Answering System

### 2010-03-05 paper/semsearch10/content/results_futurework_conclusion.tex
Hopefully done

\section{Results}
% Walk through of example query

% Results: figure 1  
\begin{figure}[t]
\centering
\includegraphics[width=85mm]{screen_intro.eps}
\caption{Introductory screen}
\label{fig:screen_intro}
\end{figure}

Initially, the user enters a query of interest, much as one would ask a question. When the user submits the query, the query is broken down into constituent parts of who, what when, and where. From there, a relevant answer is produced to respond to the requested information.

@@

After execution, the user is presented with a list of relevant answers and a depiction of how the query was parsed. In the above example, the query about tire size was executed and the most relevant result has been returned and displayed. 
Furthermore, the sequence of pages visited during execution are displayed as well.

>>>>

\section{Sample Execution}
% Walk through of example query

% Results: figure 1  
\begin{figure}[t]
\centering
\includegraphics[width=85mm]{screen_intro.eps}
\caption{Morpheus input screen}
\label{fig:screen_intro}
\end{figure}

Figure \ref{fig:screen_intro} shows the Morpheus input screen, which
allows a user to ask a question.  The user enters a natural language
question and the system follows the question answering process outlined
in this document.

@@

Figure \ref{fig:screen_result} shows the results of answering the question ``A 1997 Toyota Camry V6 needs what size tire?''
In response to this question, the user is presented with a list of relevant answers and a depiction of how the query was parsed. In the above example, the query about tire size was executed and the most relevant result has been returned and displayed. 
Furthermore, the sequence of pages visited during execution is displayed as well.

Categories are assigned to the query's SSQ contexts using the method described in section \ref{sec:terms}. The prior probabilities for a variety of categories
together with the likelihood and posterior probabilities for the term \emph{Camry}, e.g. $p(Camry | Automobiles)$ and $p(Automobiles | Camry )$, are as
shown in Table \ref{tab:prob}.
The QRM used to answer this query is selected based on the SSQ matching
process described in section \ref{sec:oqom}.
\begin{table}
  \begin{tabular}{ | l | l | c | r | }
    \hline
    Category & Prior & Likelihood & Posterior \\ \hline
    Automobiles & 0.59 & 3.48e-05 & 0.96 \\ 
    Motorcycles & 0.13 & 2.26e-06 & 0.01 \\
    Internet search engines & 0.16 & 6.29e-07 & 0.004 \\ 
    Lists of countries & 0.06 & 1.50e-06 & 0.01 \\
    Tires & 0.05 & 3.60e-06 & 0.02 \\
    \hline
  \end{tabular}
\caption{Term/Category Probabilities}
\label{tab:prob}
\end{table}
